### 2024-08-24 paper.tex
start big dimension calculation

\begin{lemma}
    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    First we compute
    \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
    Now, we have \(s(L) = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}, ...]\).
    Let \(L' = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., q_{i_2} + p_{i_3}, ..., q_{i_r} + p_{i_{r + 1}}]\).
    We compute 
    \[\gamma(s(L)) - \gamma()\]
    yep and so on
\end{proof}

>>>>

\begin{lemma}
    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    First we compute
    \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
    Now, we have \(s(L) = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}, ...]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be like \(\mu\), but with \(q_{i_x} + p_{i_{x + 1}}\) replaced by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    We compute 
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 0}^{r - 1} p_{i_{k + 1}} (\#\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_{k + 1}} + p_{i_{k + 2}}\} + 1) = \]
    \[\sum_{k = 0}^{r - 1} \#\{i : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_{k + 1}} + p_{i_{k + 2}}\}.\]
    We compute 
    \[\gamma(s(L')) - \gamma(L') = \]
    \[q_{i_0} \#\{i \notin I : q_{i_k} + p_{i_1} > \lambda_i \geq q_{i_0} \} - \sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} \lambda_i + \]
    \[\sum_{k = 0}^s \left[q_{i_k} + p_{i_k}\#\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\} - \sum_{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}} \lambda_i\right] = \]
    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (q_{i_0} - \lambda_i) + \sum_{k = 0}^s \left[q_{i_k} + \sum_{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}} (p_{i_k} - \lambda_i)\right] = \]
    \[\sum_{i : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (q_{i_0} - \lambda_i) + \sum_{k = 0}^s \sum_{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}} (p_{i_k} - \lambda_i).\]
    TODO: there are some errors with the above calculation.
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(s(L))] + [\gamma(s(L')) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        something
    \end{align*}
